### 2017-04-04 paper/evaluation.tex
removed unnecessary content
adjusting rq5

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.  From the
Maven output, we capture the parameters related to parallelism
configurations and mapped these configurations to a parallelization
mode.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.  From the \numMedLong{} projects, we
identified \numProjectsPar{} projects with parallel execution enabled
by default.  Figure~\ref{tab:freqmodes-dynamic} summarizes our
findings.

@@

To understand why developers prefer not use parallel test execution,
we considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the
\numNonParallel{} projects.
There were \emailsAnswered{} replies, and \emailsTrueAnswers{} of
those were answering the survey.

@@

From the valid replies, we confirmed that the projects we sent the
e-mails takes more than 1 minute to run tests and \emailsSeq{}
confirmed that those projects do not use parallel testing using Maven
Surefire. The other projects that we do not confirm, need and extra
parameter to execute in parallel mode \Luis{make sure that they are
inside the static analysis sheets made before}.

We noticed that \pctEmailsCI{} of developers use an continuous integration 
server to run tests, \pctEmailsLocal{} run tests in the
development machine, \pctEmailsDidNotSpecify{} did not specified their
testing setup.
We also noticed that one project has testing enabled without parallel 
configuration, however, the maintainers never run the test. 
Considering developers did not know about the existence of the
parallelism configuration \pctEmailsDoNotKnow{} of the replies
confirmed that. Three of the developers also confirmed that they use
another method of parallelization with distributed build machines.

>>>>

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.  From the \numMedLong{} projects, we
identified \numProjectsPar{} projects with parallel execution enabled
by default.  Figure~\ref{tab:freqmodes-dynamic} summarizes our
findings.

@@

To understand why developers prefer not use parallel test execution,
we considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the
\numNonParallel{} projects.
There were \emailsAnswered{} replies from \emailsProjectsAnswered{}, 
and \emailsFalseAnswers{} was not able to explain how the testing works.

@@

From the valid replies, we confirmed that the projects takes more than
\Fix{1m} to run tests and \emailsSeq{} confirmed that those projects do not use 
parallel testing using Maven Surefire. The other projects that we do not 
confirm, need and extra parameter to execute in parallel mode \Luis{make 
sure that they are inside the static analysis sheets made before}.

We noticed that \pctEmailsCI{} of developers use an continuous integration 
server to run tests, \pctEmailsLocal{} run tests in the
development machine, \pctEmailsDidNotSpecify{} did not specified their
testing setup. We also observed that one project has testing enabled 
without parallelization. However the maintainers do not execute the tests.
Considering developers did not know about the existence of the
parallelism configuration \pctEmailsDoNotKnow{} of the replies
confirmed that. Three of the developers also confirmed that they use
another method of parallelization with a distributed build machines.
